The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-25 dit-paper_ieee.tex

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). Each point on the graph is based on an average over 5000 tests.
	Note that the value of the CDF has a greater influence on this ratio than
	the system's total utilization, but less so when the CDF is higher. It is also
	important to note that even though a 0.95 ratio may not seem much, the
	synchronous C-spaces of the systems contain many dominated WCET vectors, and
	only those that are in the border (i.e. non-dominated) actually matter to the
	designer of the system. Using the asynchronous C-space instead will relax some
	constraints and therefore add new acceptable solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the C-space border.

@@

In this paper, we presented a general approach to define the C-space of a constrained periodic task set for EDF on uniform platform. Possible future works includes an extension to the study of systems with preemption costs or running on multiprocessor platforms, as the value of the DIT does not depend on preemptions or the number of processors.

@@

>>>>

	The ratio between the size of the synchronous and asynchronous C-spaces of
	these systems roughly range from 0.95 in the worst case (high utilization, high
	CDF) to 0.85 in the best case (low utilization, low CDF). Each point on the graph is an average over 5000 tests.
	Note that the value of the CDF has a greater influence on this ratio than
	the system's total utilization, but less so when the CDF is higher. It is also
	important to note that even though a 0.95 ratio may not seem much, the
	synchronous C-spaces of the systems contain many dominated WCET vectors, and
	only those that are in the border (i.e. non-dominated) actually matter to the
	designer of the system. Using the asynchronous C-space instead will relax some
	constraints and therefore add new acceptable solutions that will dominate solutions that were previously non-dominated,
	increasing the quality of the C-space border.

@@

In this paper, we presented a general approach to concisely define the C-space of a constrained periodic task set for EDF on uniform platforms. We then used the C-space to quantify the feasibility gain given by random offset values, with a final result of about 10~\% more WCET values being feasible. Possible future works includes an extension to the study of systems with preemption costs or running on multiprocessor platforms, as the value of the DIT does not depend on preemptions or the number of processors.

@@

% A mettre quelque part : nombre de contraintes avant/apres dans les expériences (issue #20)

% Future works could also study the case of offset-free systems, where the offset values can be chosen. The performance of algorithms such as \cite{grenier2008pushing} and \cite{goossens2003scheduling} (although the latter depends on the execution times), which determine offset values with optimal feasibility, can be expressed using the C-space.
